\documentclass[10pt]{article} %you need this
\usepackage{amsmath}

\author{Sheldon Deacon, 20039867}
\title{Make a latex document for Assignment 0}
\date{20 February 2018}

\begin{document}
\maketitle

\section{Instructions} %The *  removes the numbers for the sections

You must reproduce this document \textit{exactly} in LaTeX. Use the artical class with
the 10pt and a4paper options. however, you must substitute your own name and
surename for mine in the title, and use your own student number in the place of
the "12345678". You will notice that I literally will test all the different
text typesettings options that we covered in the course (and some more), and
then also---of course -- your mathe-ma-ti-cal typesetting proficiency.1
\textbf{Submission} You have to hand in on sunLearn both the \underline{pdf} copy and your latext
source, before you leave the venue.

\section{Some mathematics to typeset}
The text and mathematics below is not supposed to make sense! We just want to
look at the typesetting possiblities of latex.


\subsection{Symbols and layout}
We can either use symbols like $\phi$ and $\pi$ in the text mode, or we can write it in
the display mode like this:
\begin{equation*}
	\phi \quad and \quad \pi.
\end{equation*}
 
\subsection{Superscripts and subscripts}
Type in this formula:
\begin{equation*}
	x^{2} + y^{2+x} \quad \underrightarrow{\infty} \quad x^{2x^{y+1}}
\end{equation*}
$\qquad$Sums are also useful:$\sum_{i=0}^n \sum_{j=0}^m x^{ij} + x^{i}$, and so are
limits and integrals:
\begin{equation*}
	\int_a^{b} \frac{x^{3} - x^{4}}{f'(x)g(x)} dx \leq \lim_{x \rightarrow
	\infty} f(x).
\end{equation*}
$\qquad$Be aware of the spacing in the equations above.

\subsection{And some last technical playsetting}

\begin{equation*}
	\sqrt[5]{\frac{f^{2}(x)}{\sqrt{g(x)!}}}
\end{equation*}
and
\begin{equation*}
	\exists k : k < 42\% 
\end{equation*}
and
\begin{equation*}
	A \cup B \neq A \cap B.
\end{equation*}

\end{document}
