\documentclass[10pt]{article} %you need this
\usepackage{amsmath}

\author{Sheldon Deacon 20039867}
\title{Assignment 1}
\date{}

\begin{document}
\maketitle

You must reproduce this document exactly. Use the article class with the
10pt and a4paper options. However, you must substitute your own name and
surname for XXX in the title, and use your own student number in the place
of “12345678”. Submission: You have to hand in printed copies of both your
\LaTeX \space source, and the corresponding pdf document, before you leave the venue.

\section{My favorite Things}
My favorite quote is:
\begin{quote}
It is not the critic who counts; not the man who points out how
the strong man stumbles, or where the doer of deeds could have
done them better. The credit belongs to the man who is actually
in the arena, whose face is marred by dust and sweat and blood;
who strives valiantly; who errs, who comes short again and again,
because there is no effort without error and shortcoming; but who
does actually strive to do the deeds; who knows great enthusiasms,
the great devotions; who spends himself in a worthy cause; who at
the best knows in the end the triumph of high achievement, and who
at the worst, if he fails, at least fails while daring greatly, so that
his place shall never be with those cold and timid souls who neither
know victory nor defeat. -- \textit{Theodore-Roosevelt}
\end{quote}

.\newline I love the following movies:
\begin{enumerate}
\item Back to the Future
\item Back to the Future I
\item Back to the Future II
\end{enumerate}

. \newline Here is an interesting equation:
\begin{equation}
	\int_0^{5} x^{2} dx
	\label{eq1}
\end{equation}

.\newline I simply love Eq. \ref{eq1}.\newline
I can also recommend reading \cite{cohn}.\newline
Table \ref{t:nice} contain all my lucky numbers.

\begin{center}
\end{center}

\ref{t:nice}

\begin{table*}[h]
\begin{center}
\begin{tabular}{||cccc||}
\hline
Column 1 & Column 2 & Column 2 & Column 3 \\
\hline
\hline
 3331 & 4446 & 87837 & 78733 \\
 2333 & 7 & 78  & 5415\\
 311 & 545 & 77833 & 7507 \\
 422 & 545 & 18744 & 7560\\
 533 & 88 & 78833 & $\pi$ \\	
 \hline
\end{tabular}

\end{center}
\caption[Nice table]{My favorite numbers.}
\label{t:nice}
\end{table*}


\begin{thebibliography}{0}
\bibitem{cohn} P. M. Cohn. 2003. \emph{Basic Algebra: Groups,
Rings and Fields}. Berlin: Springer-Verlag.
\end{thebibliography}


\end{document}
